Autogenerated Questions Paper Draft

### 2018-04-04 paper_draft/paper_draft.tex
Format code snippets

%\usepackage{listings}
%\usepackage{fancyvrb}
%\usepackage{verbatim}

@@

\hfill \par
%TODO: change font here
::Dynamic Expressions Level 1 \#005:: \par
Solve the following problem: \par
\textless pre\textgreater int item = 4; \par
int bar = item / 3 - 3;\textless /pre\textgreater \par
What is the variable "bar" equal to? \par
	\{ \par
	=-2 \par
	\~{}-0.5 \par
	\~{}-1.667 \par
	\~{}1.5 \par
	\~{}0 \par
	\}
\hfill \par

@@

This first category is the simplest of all the questions here. The main objective of the question is to test students' knowledge on identifier syntax in C++.
All difficulties are also the same, just with a differing length of string, which only contributes a small amount to the essence of the question, so we'll consider
them all at once.
Here is an example of the true/false question:

\hfill \par
%TODO: change format
Is the following a valid C++ identifier? \par
Tb306wN

\hfill \par

@@

\hfill \par
What is the result of the following logical expression? \par
int numbers = 3; \par
int marks = 8; \par
(numbers \textless= 4) == (marks \textless= 10) \par

\hfill \par

@@

\hfill \par
int documents = 8; \par
int bar = 10; \par
(bar \textless = documents) != (10 \textless 9) \par
\hfill \par

@@

\hfill \par
What is the variable "bar" equal to? \par
int foo = 2; \par
int bar = foo * 4 \% 3 + 7; \par
\hfill \par

@@

%TODO: fix format like all other examples
% also pay attention to the indentation
\hfill \par
How many times does the `*' print? \par
for (int b = 4; b \textless{}  7; b = b + 1) \par
\{ \par
\indent\indent cout \textless\textless{} `*'; \par
\} \par
\hfill \par

@@

\hfill \par
How many times does the `*' print? \par
int j = 53; \par
do \par
\{
\indent\indent cout \textless\textless{} `*'; \par
\indent\indent j = j - 5; \par
\} while (j \textgreater = 30); \par
\hfill \par

@@

\hfill \par
How many times does the '*' print? \par
int i = 13; \par
while (i \textgreater = 3) \par
\{
\indent\indent cout \textless\textless{} '*'; \par
\indent\indent i /= 2; \par
\}

@@

\hfill \par
How many times does the '*' print? \par
for (int i = 43; i \textgreater= 20; i = i - 10) \par
\{ \par
\indent\indent for (int j = 56; j \textgreater 45; j = j - 5) \par
\indent\indent \{ \par
\indent\indent \indent\indent cout \textless\textless{} '*'; \par
\indent\indent \} \par
\} \par

@@

\hfill \par
What is the following output of the code? \par
int b = 61; \par
do \par
\{ \par
\indent\indent cout \textless\textless{} b \textless\textless{} ` '; \par
\indent\indent b = b - 10; \par
\} while (b \textgreater 20); \par
\hfill \par

@@

\hfill \par
What is the value of ``bar" after the switch case block? \par
int bar = 4; \par
switch (bar) \{ \par
\indent\indent case 2: \par
\indent\indent \indent\indent bar = 5; \par
\indent\indent \indent\indent break; \par
\indent\indent case 4: \par
\indent\indent \indent\indent bar = 6; \par
\indent\indent case 1: \par
\indent\indent \indent\indent bar = 2; \par
\indent\indent \indent\indent break; \par
\indent\indent case 3: \par
\indent\indent \indent\indent bar = 0; \par
\indent\indent case 0: \par
\indent\indent\indent\indent bar = 1; \par
\indent\indent\indent\indent break; \par
\} \par
\hfill \par

@@

\hfill \par
What are the contents of the array after the following statements? \par
int bar[6] = \{6, 5, 3, 8, 1, 9\}; \par
int temp; \par
temp = bar[4]; \par
bar[4] = bar[1]; \par
bar[1] = temp; \par
\hfill \par

@@

\hfill \par
What are the contents of the array after the following?\par
int documents[6] = \{3, 3, 10, 1, 1, 2\};\par
for (int i = 0; i \textless{} 6; i += 1)\par
\{ \par
\indent\indent documents[i] += 5; \par
\} \par
\hfill \par

@@

\hfill \par
What is printed after the following statements? \par
int dogs[6] = \{0, 1, 7, 3, 0, 2\}; \par
for (int i = 1; i \textless{} 4; i = i + 1) \par
\{ \par
\indent\indent cout \textless\textless{} dogs[i] \textless\textless{} " ";\par
\} \par
\hfill \par

@@

%TODO
\hfill \par
Given the following function definition: \par
int Pow() \par
\{ \par
	return 4.5 + 1.0; \par
\} \par
What is printed from the following call? \par
cout << Pow() << endl; \par
\hfill \par

@@

\hfill \par
Given the following function definition:\par
float Switch(float a, int b)\par
\{\par
    return a - b;\par
\}\par
What is printed from the following call?\par
cout << Switch(3.5, 1.5) << endl;\par
\hfill \par

@@

\hfill \par
Given the following function definition:\par
void Calculate(int\& a, int\& b, int c)\par
\{\par
	b = a / b + c;\par
\}\par

What value is printed after the following statements?\par
int marks = 5;\par
int matrix = 4;\par
int item = 5;\par
Calculate(marks, matrix, item);\par
cout << matrix << endl;\par
\hfill \par

>>>>

\usepackage{courier}
\usepackage{listings}
\lstset{basicstyle=\ttfamily}

\usepackage{fancyvrb}

@@

\begin{Verbatim}[tabsize=4]
::Dynamic Expressions Level 1 #005::
Solve the following problem: 
<pre> int item = 4; 
int bar = item / 3 - 3;</pre>
What is the variable "bar" equal to?
	{ 
	=-2 
	~-0.5 
	~-1.667 
	~1.5 
	~0 
	}
\end{Verbatim}

@@

This first category is the simplest of all the questions here. The main objective of the question is to test students' knowledge on identifier syntax in C++.
All difficulties are also the same, just with a differing length of string, which only contributes a small amount to the essence of the question, so we'll consider
them all at once.
Here is an example of the true/false question:
\begin{Verbatim}
Is the following a valid C++ identifier?
Tb306wN 
\end{Verbatim}

@@

\begin{Verbatim}
What is the result of the following logical expression? 
int numbers = 3; 
int marks = 8; 
(numbers <= 4) == (marks <= 10) 
\end{Verbatim}

@@

\begin{lstlisting}[language=C++]
int documents = 8;
int bar = 10;
(bar < = documents) != (10 < 9)
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
What is the variable "bar" equal to? 
int foo = 2; 
int bar = foo * 4 % 3 + 7; 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
How many times does the '*' print? 
for (int b = 4; b < 7; b = b + 1)
{
	cout << '*';
} 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
How many times does the '*' print? 
int j = 53;
do 
{
	cout << '*'; 
	j = j - 5; 
} while (j >= 30); 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
How many times does the '*' print?
int i = 13; 
while (i >= 3) 
{
	cout << '*'; 
	i /= 2;
}
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
How many times does the '*' print? 
for (int i = 43; i >= 20; i = i - 10) 
{ 
	for (int j = 56; j > 45; j = j - 5) 
	{ 
		cout << '*'; 
	} 
}
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
What is the following output of the code? 
int b = 61; 
do
{ 
	cout << b << ' '; 
	b = b - 10; 
} while (b > 20); 
\end{lstlisting}

@@

%\begin{Verbatim}
%What is the value of "bar" after the switch case block?
%\end{Verbatim}
%\begin{lstlisting}[language=C++]

\begin{lstlisting}[language=C++]
What is the value of "bar" after the switch case block?
int bar = 4; 
switch (bar) { 
	case 2: 
		bar = 5; 
		break; 
	case 4: 
		bar = 6; 
	case 1: 
		bar = 2;
		break; 
	case 3: 
		bar = 0; 
	case 0: 
		bar = 1; 
		break; 
} 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
What are the contents of the array after the following statements? 
int bar[6] = {6, 5, 3, 8, 1, 9}; 
int temp; 
temp = bar[4]; 
bar[4] = bar[1]; 
bar[1] = temp; 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
What are the contents of the array after the following?
int documents[6] = {3, 3, 10, 1, 1, 2};
for (int i = 0; i < 6; i += 1)
{ 
	documents[i] += 5; 
} 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
What is printed after the following statements?
int dogs[6] = {0, 1, 7, 3, 0, 2}; 
for (int i = 1; i < 4; i = i + 1) 
{ 
	cout << dogs[i] << " ";
} 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
Given the following function definition:
int Pow() 
{ 
	return 4.5 + 1.0; 
} 
What is printed from the following call? 
cout << Pow() << endl; 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
Given the following function definition:
float Switch(float a, int b)
{
    return a - b;
}
What is printed from the following call?
cout << Switch(3.5, 1.5) << endl;
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
Given the following function definition:
void Calculate(int& a, int& b, int c)
{
	b = a / b + c;
}

What value is printed after the following statements?
int marks = 5;
int matrix = 4;
int item = 5;
Calculate(marks, matrix, item);
cout << matrix << endl;
\end{lstlisting}
